preliminary_regression

### 2021-12-11 preliminary_analysis.Rmd
change in regressions

reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
stargazer(reg3, type = 'text')
```
# Swing

@@

reg5 <- felm(incumbent_vote_share ~ treat_post | city + year_int , 
             data = election_all5)

reg6 <- felm(change_vote ~ treat_post | city + year_int, 
             data = election_all5)

@@

stargazer(reg4_1, reg4_2, reg4_3, reg4_4, type = 'text')
```

>>>>

reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
stargazer(reg3, type = 'text',
          title = c("Effects of a Catastrophic Event on Voter Turnout"),
          column.labels = c('Voter Turnout'),
          covariate.labels = c('Treatment Effect'),
          dep.var.labels = c(''))
```
# Swing

@@

reg5 <- felm(incumbent_vote_share ~ treat_post | city + year_int + election_type , 
             data = election_all5)

@@

stargazer(reg4_1, reg4_2, reg4_3, reg4_4, type = 'text')

reg5_1 <- felm(percent_turnout ~ treat_post_kurdish | city + year_int, 
             data = dummies)
reg5_2 <- felm(percent_turnout ~ event_earthquake | city + year_int, 
             data = dummies)
reg5_3 <- felm(percent_turnout ~ treat_post_cyprus | city + year_int, 
             data = dummies)
reg5_4 <- felm(percent_turnout ~ treat_post_refugee | city + year_int, 
             data = dummies)

stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'text')
```
